\documentclass[letterpaper,12pt]{report}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{fancyhdr,tocloft,natbib,url,graphicx,float,listings,sidecap,wrapfig}
\usepackage[font=small,labelfont=bf,labelsep=period]{caption}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usepackage{qtree,algorithm,algorithmic}
\usepackage{natbib}
\usepackage[table]{xcolor}
\usepackage{xcolor}
\usepackage{listings}
\pagestyle{plain}
\fancyhf{}
\lhead{}
\chead{}
\rhead{}
\cfoot{\thepage}

%\floatstyle{boxed}
%\restylefloat{figure}

\hypersetup {
	colorlinks=false,
	pdfborder={0 0 0},
}

\setcounter{secnumdepth}{3}
\renewcommand*\thesection{\arabic{section}.}
\renewcommand*\thesubsection{\thesection \arabic{subsection}.}
\renewcommand*\thesubsubsection{\thesubsection \arabic{subsubsection}.}

\setcounter{tocdepth}{3}
\renewcommand\contentsname{}				% TOC title
\renewcommand\listfigurename{}				% LOF title
\renewcommand\listtablename{}				% LOT title
\setlength\cftaftertoctitleskip{-0.5in}
\setlength\cftafterloftitleskip{-0.5in}
\setlength\cftafterlottitleskip{-0.5in}

\renewcommand\bibsection{\section{References}}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.65, 0.12, 0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{codestyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{blue},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=codestyle}

\lstdefinelanguage{yaml}{
    keywords={true,false,null},
    sensitive=false,
    comment=[l]{\#},
    morecomment=[s]{/*}{*/},
    moredelim=**[il][\color{red}\mdseries{:}\color{blue}\mdseries]{:},   % switch to value style at :
}

\begin{document}

\hypersetup{pageanchor=false}
%%  COVER PAGE
\input{cover}	
\clearpage

%% SIGNATURE PAGE
\input{signature}
\clearpage

\hypersetup{pageanchor=true}
\setcounter{page}{1}
\pagenumbering{roman}
\renewcommand\arraystretch{1.5}

%% ABSTRACT
\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}
Wendorf, Bennett, ``NeuraViz: A Web Application For Visualizing Artificial Neural Network Structures,'' Master of Software Engineering, May 2024, (Jason Sauppe, Ph.D.). \\

This manuscript describes the software engineering processes and principles adhered to during the development of Neuraviz, a web application for visualizing artificial neural network structures. Users upload pre-trained machine learning models from popular frameworks including Pytorch and Keras, and Neuraviz generates a visual representation of the model's architecture. The following manuscript focuses on the design, implementation, testing, and deployment of NeuraViz in an effort to comprehensively encapsulate the entire development process.
\clearpage

%%% ACKNOWLEDGEMENTS
\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgments}
I would like to extend my sincerest thanks to my project advisor, Dr. Jason Sauppe, for his guidance and support throughout the development of NeuraViz. His feedback was always crucial in pointing me in the right direction, especially when I was overwhelmed with possibilities. 

Thank you also to the entire computer science department at the University of Wisconsin-La Crosse for tirelessly helping me through all my coursework and projects throughout my tenure at the university. My ability to complete this monumental task would not have been possible without them.

I would also like to thank the open source community for providing the tools and resources used in this project. Open source software is an integral part of the modern software space and none of our lives would be the same without it.

Finally, I would like to thank my parents, family, friends, and all the teachers, mentors, and colleagues who have helped, supported, and encouraged me throughout my life. I am more grateful thank I can possibly express in words.
\clearpage

%% TABLE OF CONTENTS
\section*{Table of Contents}
\tableofcontents
\clearpage


%% LIST OF TABLES
\section*{List of Tables}
\addcontentsline{toc}{section}{List of Tables}
\listoftables
\clearpage

%% LIST OF FIGURES
\section*{List of Figures}
\addcontentsline{toc}{section}{List of Figures}
\listoffigures
\clearpage

%% GLOSSARY
\section*{Glossary}
\addcontentsline{toc}{section}{Glossary}
\input{glossary}
\clearpage

\setcounter{page}{1}
\pagenumbering{arabic}

\IfFileExists{01_introduction/introduction}{\input{01_introduction/introduction}}{}\clearpage
\IfFileExists{02_dev_process/software_development_process}{\input{02_dev_process/software_development_process}}{}\clearpage
\IfFileExists{03_design/design}{\input{03_design/design}}{}\clearpage
\IfFileExists{04_implementation/implementation}{\input{04_implementation/implementation}}{}\clearpage
\IfFileExists{05_testing/testing}{\input{05_testing/testing}}{}\clearpage
\IfFileExists{06_security/security}{\input{06_security/security}}{}\clearpage
\IfFileExists{07_conclusion/conclusion}{\input{07_conclusion/conclusion}}{}\clearpage

%% BIBLIOGRAPHY
\bibliographystyle{plain}
\bibliography{bibliography}
\clearpage

%%% APPENDICES
\section{Appendices}
\label{sec:appendices}
\clearpage

\end{document}
