\subsection*{Artificial Neural Network}
A computational model that is inspired by the way biological neural networks in the human brain process information. It is composed of layers of nodes, each of which is connected to the next layer via links. Each connection has a weight associated with it, and the network learns by adjusting these weights based on the input data. The network can be trained to recognize patterns in data, make predictions, and perform other tasks.

\subsection*{Activation Function}
A function that determines the output of a node in a neural network based on the weighted sum of its inputs. Common activation functions include the sigmoid function, the hyperbolic tangent function, and the rectified linear unit (ReLU) function. The activation function introduces non-linearity into the network, allowing it to learn complex patterns in the data.

\subsection*{\LaTeX{}}
\LaTeX{} is a document markup language for the TeX typesetting program.

\subsection*{TikZ}
TikZ is a graph drawing package for \LaTeX{} that allows users to create high-quality diagrams and illustrations.

\subsection*{Scalable Vector Graphics (SVG)}
SVG is an XML-based vector image format for two-dimensional graphics with support for interactivity and animation. It is commonly used in web applications.

\subsection*{Raster Graphics}
Raster graphics are digital images composed of a grid of pixels. Each pixel has a specific color value, and the image is displayed by rendering the pixels on a screen. Common raster graphics formats include JPEG, PNG, and GIF.

\subsection*{Python}
Python is a high-level programming language known for its simplicity and readability. It is widely used in data science, machine learning, web development, and other fields.

\subsection*{PyTorch}
PyTorch is a popular open-source machine learning library for building artificial neural networks. It is known for its flexibility and ease of use, making it a popular choice for researchers and developers.

\subsection*{Keras}
Keras is an open-source deep learning library written in Python that provides a high-level interface for building and training neural networks. Distributed by the Tensorflow team, it is a high-level API on top of Tensorflow and other popular frameworks.

\subsection*{TypeScript}
TypeScript is a superset of JavaScript that adds static typing and other features to the language. It is commonly used in web development to improve code quality and maintainability.

\subsection*{Parsing}
Parsing is the process of analyzing a sequence of symbols to determine its grammatical structure. In the context of this project, it refers to the process of extracting information from a machine learning model object to generate a visual representation of the model's architecture.

\subsection*{Sprint}
A sprint is a short, time-boxed period during which a development team works to complete a set amount of work. Sprints are a key component of the Scrum agile framework and are typically 1-4 weeks long.

\subsection*{JavaScript Object Notation (JSON)}
JSON is a lightweight data interchange format that is easy for humans to read and write and easy for machines to parse and generate. It is commonly used to transmit data between a server and a web application.